First Exclusive Measurement of Deep Virtual Compton Scattering off $^4$He: Toward the 3D tomography of nuclei

### 2017-04-20 eg6-letters/coherent/dvcs_he4_prl.tex
change the scale of fig 2 in the coherent prl

%
\date{\today}
\begin{abstract}
We report the first fully exclusive measurement of coherent deeply virtual 
Compton scattering off a nucleus for $A>1$. The experiment used the 6 GeV 
electron beam from the CEBAF machine at Jefferson Lab incident on a $^4$He gas 
target in the center of the CEBAF large acceptance spectrometer. A new radial 
time projection chamber (RTPC) was used to detect the recoiling $^4$He
nuclei and ensure the exclusivity of the process. The measured beam spin 
asymmetries are larger than that observed on the proton in the same kinematic 
domain. Since $^4$He is a spin zero target, we were able to extract, in a 
completely model independent way, the real and imaginary parts of the $^4$He 
Compton form factors, $\cal H_A$, which are functions of the generalized parton 
distribution $H_A$. This pioneering measurement of coherent deeply virtual 
Compton scattering on the $^4$He nucleus, with a fully exclusive final state 
via nuclear recoil tagging, leads the way toward 3D imaging of the partonic 
structure of nuclei.
\end{abstract}
\pacs{Valid PACS appear here}

@@

The most promising way to access GPDs experimentally is through the measurement 
of deeply virtual Compton scattering (DVCS), \textit{i.e.}, the hard exclusive 
electroproduction of a real photon.  While other processes are known to be 
sensitive to GPDs, the measurement of DVCS is considered the cleanest probe and 
has been the focus of worldwide efforts 
\cite{Stepanyan:2001sm,Airapetian,Chekanov:2003ya,Aktas:2005ty,Chen:2006na,Munoz 
Camacho:2006hx,Girod:2007aa,Mazouz:2007aa,Gavalian:2009,Seder:2015,Pisano:2015,Jo:2015ema} 
involving several accelerator facilities such as Jefferson Lab, HERA and  CERN.  
The vast majority of these measurements focused on the study of proton 
structure and allowed for an extraction of the three-dimensional picture of the 
nucleon (for details on the formalism, see 
\cite{Goeke:2001tz,Diehl:2003ny,Ji:2004gf,Belitsky:2005qn,Boffi:2007yc,Guidal:2013rya}).
This framework is also applicable to nuclei, giving access to completely new 
information about nuclear structure in terms of quarks and 
gluons \cite{Dupre:2015jha}.
Study of the 3D structure of nuclei appears to be especially important
in light of the large nuclear effects observed in nuclear parton distribution 
functions \cite{Geesaman:1995yd,Norton:2003cb,Hen:2016kwk}.

\begin{figure}[tb]
\includegraphics[width=6.5cm]{figs/DVCS_diagram.pdf}
\caption{Representation of the leading order hand-bag diagram of the DVCS 
process off $^4$He.}
\label{fig:diags}
\end{figure}

One must overcome two major experimental challenges in measuring coherent 
nuclear DVCS, $eA\rightarrow^\prime A^\prime\gamma$. First, the cross section 
of coherent scattering is suppressed due to the nuclear form factor, and 
second, the recoil nucleus ($A^\prime$) must be detected to ensure coherence.  
FIG.~\ref{fig:diags} illustrates the hand-bag diagram for coherent DVCS on 
$^4$He. Similar to the proton case, at large virtual photon's 4-momentum square 
$Q^2=-(k-k')^{2}$ and small squared momentum transfer $t=(p-p')^{2}$ (in terms 
of the electron, $k(k')$, and $^4$He, $p(p')$, four-vectors), the DVCS handbag 
diagram can be factorized into two parts \cite{Freund_Collins,Ji_Osborne}. The 
hard part includes the photon-quark interaction and is calculable in 
perturbative QCD. The non-perturbative part is parametrized in terms of GPDs, 
which embed the partonic structure of the hadron. The GPDs depend on the three 
variables $x$, $\xi$, and $t$ as introduced in FIG.~\ref{fig:diags}. The 
parameter $\xi$ relates to the Bjorken variable $x_{B}$: $\xi\approx 
{{x_B}\over{2-x_B}}$, where $x_B=\frac{Q^2}{2M\nu}$, $\nu=k^0-k^{0\prime}$, and 
$M$ is the proton mass. The parameter $x$ is the quark's internal loop momentum 
fraction and cannot be accessed experimentally. We in fact measure 
Compton form factors (CFF) \cite{Guidal:2013rya}, which are
complex amplitudes defined as:

@@

Until now, the only available data on nuclear DVCS was from the HERMES 
experiment \cite{Ellinghaus:2002zw}, where coherence in the reaction was based 
only on kinematic cuts on the measured scattered electron and real photon. That 
measurement was performed on a large set of nuclei ($^4$He, N, Ne, Kr and Xe), 
but the mixing of the coherent and incoherent processes could affect the
measurement significantly \cite{Guzey:2003jh}. In this regard, direct detection 
of the low-energy recoil nucleus is the best way to guarantee that the nucleus 
remains intact. The CEBAF large acceptance spectrometer (CLAS) in Hall-B at 
Jefferson Lab has been previously used for DVCS measurements on nucleon
\cite{Girod:2007aa,Gavalian:2009,Seder:2015,Pisano:2015,Jo:2015ema}.

In order to measure DVCS on $^4$He with a fully exclusive final state, we built 
a specialized radial time projection chamber (RTPC) for detection and 
identification of low energy recoiling light nuclei. The $^4$He nucleus is an 
ideal experimental target in this regard, as it is light enough to be detected 
in such a setting, while it is subject to significant nuclear effects 
\cite{JSeely} and has rather high density. A helium target leads to another 
important advantage, as the number of GPDs defined for a hadron depends on its 
spin. The structure of a spin zero nucleus, such as $^4$He, is parametrized by 
only one chiral even GPD ($H_{A}(x,\xi,t)$) at leading twist, while 4 GPDs 
arise in the nucleon case. This significantly simplifies the interpretation of 
the data and allows a model independent extraction of the $^4$He CFF 
($\mathcal{H}_{A}$) presented at the end of this letter.

@@

The experiment E08-024 took place in Hall-B at Jefferson Lab in 2009 using the 
nearly 100\% duty factor, longitudinally polarized electron beam (83$\%$ 
polarization) at an energy of 6.064 GeV. The data were collected over 40 days 
using a 6 atm gaseous $^4$He target placed 64 cm upstream of the nominal center 
of CLAS. For DVCS experiments, the CLAS baseline design \cite{Mecking:2003zu} 
is supplemented with an inner calorimeter (IC) and a solenoid magnet. The IC 
extends the photon detection acceptance of CLAS to polar angles as low as 
4$^{\circ}$. The low-energy M\o{}ller electrons produced in the target form a 
very high rate background that is suppressed by a 5 Tesla solenoid magnet 
placed around the target.

In our kinematics, the recoil $^4$He nuclei produced in DVCS have a low average 
momentum around 300 MeV/c. CLAS cannot detect such low energy $\alpha$ 
particles, so in order to ensure the exclusivity of the measurement, we built a 
small and light RTPC to complement CLAS. The RTPC is a $20$ cm long cylinder 
with a diameter of $15$ cm, positioned directly around the $^4$He gaseous 
target. The target is a $25$ cm long and $6$ mm diameter Kapton straw with 
$27~\mu$m thick wall. The RTPC was calibrated specifically for the detection of 
$^4$He nuclei using elastic scattering with a 1.2~GeV electron beam.

@@

%DVCS selection
To identify coherent DVCS events, we first select events where one electron, 
one $^4$He, and at least one photon are detected in the final state. Electrons 
are identified using measured momentum, time, and energy in the fiducial volume 
of the CLAS system's drift chambers, Cerenkov counters, scintillator counters, 
and electromagnetic calorimeters. The recoiling $^4$He nuclei are identified in 
the RTPC using time, track quality, and energy loss cuts for tracks in the 
fiducial region. In addition, we apply a vertex matching cut to ensure that the 
electron and helium nucleus originate from the same position. The photons are 
detected in either the IC or the CLAS electromagnetic calorimeter. Note that 
even though the DVCS reaction has only one real photon in the final state, 
events with more than one good photon are not discarded at this stage. This is 
motivated by the fact that, while soft photons are likely to be produced in 
random coincidence, they cannot be mistaken for the large energy DVCS photons 
($>2$ GeV). The most energetic photon is always considered as the DVCS photon 
candidate.

To ensure the interaction occurs at the partonic level and the DVCS handbag 
diagram is dominant, we select events with $Q^{2}$ greater than 1 
$GeV^{2}/c^{2}$. Exclusivity of the coherent DVCS reaction is optimized by 
applying a set of cuts on the following kinematic variables: the co-planarity 
angle ($\Delta \phi$), \textit{i.e.}, the angle between the ($\gamma,\gamma^*$) 
and ($\gamma^*$,$^4$He$'$) planes, the missing energy, the missing mass 
squared, the missing transverse momentum of the $e'^4$He$'\gamma$ system, the 
missing mass squared of the $e'^4$He$'$ system, and the angle ($\theta$) 
between the measured photon and the missing momentum of the $e'^4$He$'$ system.  
The most relevant of these cuts are presented in FIG.~\ref{fig:kin-cuts}, which 
shows 3$\sigma$ cuts except for the missing energy (which appears to be too 
large and for which we reduced the cut window to [-0.45,0.5] GeV).  We also 
reject events where a $\pi^0$ is identified by invariant mass reconstruction of 
two photons. About 3200 events pass these requirements. Their kinematic 
distributions are shown in FIG.~\ref{fig:kin-coverage}.

\begin{figure}[tb]
\includegraphics[width=8cm]{figs/coh_exc_cuts.pdf}
\caption{Four of the six coherent DVCS exclusivity cuts. The black 
distributions represent the coherent DVCS events candidate. The shaded 
distributions represent the events which passed all the exclusivity cuts except 
the quantity plotted. The vertical red lines represent the applied exclusivity 
cuts. The distributions from left to right and from top to bottom are: $\Delta 
\phi$, missing energy, missing mass squared and the cone angle ($\theta$) 
between the measured and the calculated photons.}
\label{fig:kin-cuts}
\end{figure}

@@

%asymmetries
In this work, the physics observable extracted using coherent DVCS events is
the beam spin asymmetry (BSA). The BSA on an unpolarized target, $A_{LU}$, is 
measured as the difference of cross sections of the reaction at opposite beam 
helicities normalized to the total cross section:
  \begin{equation}
  A_{LU} = \frac{d^{5}\sigma^{+} - d^{5}\sigma^{-} }
                {d^{5}\sigma^{+} + d^{5}\sigma^{-}},
    \label{BSA_equation}
  \end{equation}
where $d^{5}\sigma^{+(-)}$ is the DVCS differential cross 
section for a positive (negative) beam helicity. 
In this ratio, luminosity normalization and
detector efficiencies largely cancel and $A_{LU}$ can be expressed in
terms of helicity-state yields ($N^{+/-}$)
\begin{equation}
A_{LU} = \frac{1}{P_{B}} \frac{N^{+} - N^{-}}{N^{+} + N^{-} },
\end{equation}
where $P_{B}$ is the beam polarization.

The DVCS and well-known Bethe-Heitler (BH) processes, where the real 
photon is emitted by the incoming or the outgoing lepton, have the same final 
state and are indistinguishable. The amplitude of real photon 
electroproduction is a sum of the amplitudes of these two processes. The BH 
amplitude is defined by the target form factors, while the DVCS amplitude is 
a combination of the form factors and GPDs. At our kinematics, the cross 
section of real photon electroproduction is dominated by the BH 
contribution, while the DVCS contribution is very small. Its effect is however
enhanced in the observables sensitive to the interference term, {\it e.g.} 
BSA. The three terms entering the cross section calculation,
the BH and DVCS amplitudes squared and their interference term depend on the
azimuthal angle
$\phi$ between the $(e,e^\prime)$ and $(\gamma^*,^4$He$^\prime)$ planes, as
shown for the nucleon in \cite{Belitsky:2001ns} and for the spin-zero targets
in \cite{Kirchner:2003wt,Belitsky:2008bz}. Based on this work, the BSA 
of a spin-zero hadron can be expressed as
\begin{equation}
\begin{split}
&A_{LU}(\phi) = \\
&\frac{\alpha_{0}(\phi) \, \Im m(\mathcal{H}_{A})}
{\alpha_{1}(\phi) + \alpha_{2}(\phi) \, \Re e(\mathcal{H}_{A}) + \alpha_{3}(\phi) \, 
\big( \Re e(\mathcal{H}_{A})^{2} + \Im m(\mathcal{H}_{A})^{2} \big)},
\end{split}
\label{eq:A_LU-coh}
\end{equation}
where $\Im m(\mathcal{H}_{A})$ and $\Re e(\mathcal{H}_{A})$ are the imaginary 
and real parts of the $^4$He CFF $\mathcal{H}_{A}$ and depend on the GPD $H_A$.  
The explicit expression of the kinematic factors $\alpha_i$ are written in 
\cite{Belitsky:2008bz}, they are functions of Fourier harmonics in the 
azimuthal angle $\phi$, the nuclear form factor $F_A(t)$, $Q^2$ and $x_B$,
$x_{A} = \frac{x_{B}M_{N}}{M_{A}}$, $y=\frac{Q^{2}}{2x_{A}M_{A}E_{beam}}$, and 
$\epsilon = \frac{2x_{A}M_{A}}{\sqrt{Q^{2}}}$, where $M_{A}$($M_{N}$) is the $^4$He 
(nucleon) mass. Using the different $\sin(\phi)$ and $\cos(\phi)$ contributions 
in these factors, it is possible to extract unequivocally both imaginary and real 
parts of $\mathcal{H}_{A}$ from the BSA.

In this work the azimuthal dependence of the BSA, $A_{LU}$, has been studied 
for a wide range of kinematics. We identified two main backgrounds to our 
measurement, accidental coincidences and exclusive coherent $\pi^0$ production.  
The accidentals have particles originating from different events, and we 
estimate their  contribution to be 4.1\% of our sample. We evaluated this 
contribution by selecting events passing all our cuts but with an electron and 
helium originating from different vertices. Regarding the $\pi^0$ production, 
it can easily be mistaken for DVCS when one of the two photons from the $\pi^0$ 
decay is produced at low energy in the laboratory frame and remains undetected.  
To estimate the importance of this background, we developed an event generator 
tuned on the experimental yield of exclusive $\pi^0$ measured by our 
experiment. We used this generator together with a GEANT3 simulation of our 
detector to estimate the ratio between the number of $\pi^0$ events where the 
two photons are detected and those that is misidentified as DVCS events. This 
ratio is then multiplied by the measured yield of exclusive $\pi^0$ events to 
correct the DVCS data.  Depending on the kinematics, we found contaminations of 
2 to 4\%. The study of systematic uncertainties showed that the main 
contributions come from the choice of the DVCS exclusivity cuts (8\%) and the 
large binning size (5.1\%). However, added quadratically,the total systematic 
uncertainty is about 10\%, which is significantly smaller than statistical 
uncertainties in all kinematical bins.

Due to limited statistics, dependence on the kinematical variables $Q^2$, 
$x_B$, and $t$ has been studied separately. In FIG.~\ref{fig:alu}, $A_{LU}$ for 
the three sets of binning is presented. The curves on the plots are fits with 
the function presented in Eq.~\ref{eq:A_LU-coh}, where the real and imaginary 
parts of the CFF $\mathcal{H}_{A}$ are the free parameters of the fit.  In 
FIG.~\ref{fig:alu90} the $Q^2$, $x_{B}$, and $t$-dependencies of the fitted 
$A_{LU}$ at $\phi$~=~90$^{\circ}$ are shown. The $x_{B}$ and $t$-dependencies 
are compared to theoretical calculations performed by S.~Liuti and K.~Taneja 
\cite{simonetta_2}. The model takes into account the effect on the quark 
distribution of the virtuality of the nucleon ({\it i.e.} with four-momentum 
squared not equal to the square of their mass). The calculations are at slightly 
different kinematics than our data but still provide some guidance. The 
experimental results appear to have a larger asymmetries than the calculations
in the $x_B = 0.307$ bin. The difference may arise from the theoretical 
uncertainty in the determination of the crossing point between the 
antishadowing region, where the parton nuclear distribution is larger than the 
nucleon one, and the EMC effect region, where the nuclear effect reverses its 
sign.

@@

\begin{figure}[tb]
\includegraphics[width=8cm]{figs/Coherent_CFF.pdf}
\caption{The model-independent extraction of the imaginary (top panel) and
real (bottom panel) parts of the $^4$He CFF $\mathcal{H}_A$, as functions of
$Q^{2}$ (right panel), $x_B$ (middle panel), and $t$ (left panel). The full red 
curves are calculations based on an on-shell model from
\cite{Vadim_priv}. The black-dashed curves are calculations from a convolution 
model based on the VGG model for the nucleons' GPDs \cite{Guidal_priv}. The 
blue long-dashed curve on the top-right plot is from
an off-shell model based on \cite{GonzalezHernandez:2012jv}.}
\label{fig:CFF_HA}
\end{figure}

The $Q^2$, $x_B$, and $t$ dependencies of the $^4$He CFF $\mathcal{H}_A$ 
extracted from the fit to the azimuthal dependence of $A_{LU}$ are shown in 
FIG.~\ref{fig:CFF_HA}. Curves on the graphs are model calculations, labelled 
{\it convolution} and {\it off-shell}. In the convolution model 
\cite{Vadim_priv}, the nucleus is assumed to be composed of non-relativistic 
nucleons, each interacting independently with the probe. The Convolution-Dual 
model is based on nucleon GPDs from the dual parametrization 
\cite{Guzey:2006xi}, where the Convolution-VGG uses nucleon GPDs  from the VGG 
model and is based on the double distributions ansatz \cite{DD_model}. The 
off-shell model is the same as in Figure \ref{fig:alu90} using an improved
GPD model for the nucleon \cite{GonzalezHernandez:2012jv}.

>>>>

%
\date{\today}
\begin{abstract}
We report the first fully exclusive measurement of coherent deeply virtual 
Compton scattering off a nucleus for $A>1$. The experiment used the 6 GeV 
electron beam from the CEBAF accelerator at Jefferson Lab incident on a $^4$He gas 
target in the center of the CEBAF large acceptance spectrometer (CLAS). A new radial 
time projection chamber (RTPC) was used to detect the recoiling $^4$He
nuclei and ensure the exclusivity of the process. The measured beam-spin 
asymmetries are larger than that observed on the proton in the same kinematic 
domain. Since $^4$He is a spin-zero target, we were able to extract, in a 
completely model-independent way, the real and imaginary parts of the $^4$He 
Compton form factors, $\cal H_A$, which are functions of the generalized parton 
distribution $H_A$. This pioneering measurement of coherent deeply virtual 
Compton scattering on the $^4$He nucleus, with a fully exclusive final state 
via nuclear recoil tagging, leads the way toward 3D imaging of the partonic 
structure of nuclei.
\end{abstract}
\pacs{Valid PACS appear here}

@@

The most promising way to access GPDs experimentally is through the measurement 
of deeply virtual Compton scattering (DVCS), \textit{i.e.}, the hard exclusive 
electroproduction of a real photon.  While other processes are known to be 
sensitive to GPDs, the measurement of DVCS is considered the cleanest probe and 
has been the focus of worldwide efforts 
\cite{Stepanyan:2001sm,Airapetian,Chekanov:2003ya,Aktas:2005ty,Chen:2006na,Munoz 
Camacho:2006hx,Girod:2007aa,Mazouz:2007aa,Gavalian:2009,Seder:2015,Pisano:2015,Jo:2015ema} 
involving several accelerator facilities such as Jefferson Lab, HERA, and CERN.  
The vast majority of these measurements focused on the study of proton 
structure and allowed for an extraction of the three-dimensional picture of the 
nucleon (for details on the formalism, see 
\cite{Goeke:2001tz,Diehl:2003ny,Ji:2004gf,Belitsky:2005qn,Boffi:2007yc,Guidal:2013rya}).
This framework is also applicable to nuclei, giving access to completely new 
information about nuclear structure in terms of quarks and 
gluons \cite{Dupre:2015jha}.
Study of the 3D structure of nuclei appears to be especially important
in light of the large nuclear effects observed in nuclear parton distribution 
functions \cite{Geesaman:1995yd,Norton:2003cb,Hen:2016kwk}.

\begin{figure}[tb]
\includegraphics[width=6.5cm]{figs/DVCS_diagram.pdf}
\caption{Representation of the leading order handbag diagram of the DVCS 
process off $^4$He.}
\label{fig:diags}
\end{figure}

One must overcome two major experimental challenges in measuring coherent 
nuclear DVCS, $eA\rightarrow e^\prime A^\prime\gamma$. First, the cross section 
of coherent scattering is suppressed due to the nuclear form factor, and 
second, the recoil nucleus ($A^\prime$) must be detected to ensure coherence.  
Figure \ref{fig:diags} illustrates the handbag diagram for coherent DVCS on 
$^4$He. Similar to the proton case, at large virtual photon's 4-momentum square 
$Q^2=-(k-k')^{2}$ and small squared momentum transfer $t=(p-p')^{2}$ (in terms 
of the electron, $k(k')$, and $^4$He, $p(p')$, four-vectors), the DVCS handbag 
diagram can be factorized into two parts \cite{Freund_Collins,Ji_Osborne}. The 
hard part includes the photon-quark interaction and is calculable in 
perturbative QCD. The non-perturbative part is parametrized in terms of GPDs, 
which embed the partonic structure of the hadron. The GPDs depend on the three 
variables $x$, $\xi$, and $t$ as introduced in Fig.~\ref{fig:diags}. The 
parameter $\xi$ relates to the Bjorken variable $x_{B}$: $\xi\approx 
{{x_B}\over{2-x_B}}$, where $x_B=\frac{Q^2}{2M\nu}$, $\nu=k^0-k^{0\prime}$, and 
$M$ is the proton mass. The parameter $x$ is the quark's internal loop momentum 
fraction and cannot be accessed experimentally. We in fact measure 
Compton form factors (CFF) \cite{Guidal:2013rya}, which are
complex amplitudes defined as:

@@

Until now, the only available data on nuclear DVCS was from the HERMES 
experiment \cite{Ellinghaus:2002zw}, where coherence in the reaction was based 
only on kinematic cuts on the measured scattered electron and real photon. The 
measurement was performed on a large set of nuclei ($^4$He, N, Ne, Kr and Xe), 
but the mixing of the coherent and incoherent processes could affect the
measurement significantly \cite{Guzey:2003jh}. In this regard, direct detection 
of the low-energy recoil nucleus is the best way to guarantee that the nucleus 
remains intact. The CEBAF large acceptance spectrometer in Hall-B at 
Jefferson Lab has been previously used successfully for DVCS measurements on the nucleon
\cite{Girod:2007aa,Gavalian:2009,Seder:2015,Pisano:2015,Jo:2015ema}.

In order to measure DVCS on $^4$He with a fully exclusive final state, we built 
a specialized radial time projection chamber (RTPC) for the detection and 
identification of low-energy recoiling light nuclei. The $^4$He nucleus is an 
ideal experimental target in this regard, as it is light enough to be detected 
in such a setting, while it is subject to significant nuclear effects 
\cite{JSeely} and has rather high density. A helium target leads to another 
important advantage, as the number of GPDs defined for a hadron depends on its 
spin. The structure of a spin-zero nucleus, such as $^4$He, is parametrized by 
only one chiral even GPD ($H_{A}(x,\xi,t)$) at leading twist, while 4 GPDs 
arise in the nucleon case. This significantly simplifies the interpretation of 
the data and allows a model independent extraction of the $^4$He CFF 
($\mathcal{H}_{A}$) presented at the end of this letter.

@@

The experiment E08-024 took place in Hall-B at Jefferson Lab in 2009 using the 
nearly 100\% duty factor, longitudinally polarized electron beam (83$\%$ 
polarization) at an energy of 6.064 GeV. The data were collected over 40 days 
using a 6 atm gaseous $^4$He target placed 64 cm upstream of the nominal center 
of CLAS. For DVCS experiments, the CLAS baseline design \cite{Mecking:2003zu} 
is supplemented with an inner calorimeter (IC) and a solenoid magnet. The IC 
extends the photon detection acceptance of CLAS to polar angles as low as 
4$^{\circ}$. The low-energy M\o{}ller electrons produced in the target form a 
very high rate background that is suppressed by a 5-Tesla solenoid magnet 
placed around the target.

In our kinematics, the recoil $^4$He nuclei produced in DVCS have low momentum,
averaging \~300 MeV/c. CLAS cannot detect such low energy $\alpha$ 
particles, so in order to ensure the exclusivity of the measurement, we built a 
small and light RTPC to complement CLAS. The RTPC is a $20$ cm long cylinder 
with a diameter of $15$ cm, positioned directly around the $^4$He gaseous 
target. The target is a $25$-cm-long and $6$-mm-diameter Kapton straw with 
$27~\mu$m thick walls. The RTPC was calibrated specifically for the detection of 
$^4$He nuclei by utilizing elastic scattering $e^4$He$\to e^\prime$$^4$He with
a 1.2~GeV electron beam.

@@

%DVCS selection
To identify coherent DVCS events, we first select events where one electron, 
one $^4$He, and at least one photon are detected in the final state. Electrons 
are identified using their measured momentum, time, and energy obtained from 
the CLAS drift chambers, Cerenkov counters, scintillator counters, 
and electromagnetic calorimeters. The recoiling $^4$He nuclei are identified in 
the RTPC using time, track quality, and energy-loss cuts for tracks in the 
fiducial region. In addition, we apply a vertex-matching cut to ensure that the 
electron and helium nucleus originate from a common reaction vertex in the target cell. The photons are 
detected in either the IC or the CLAS electromagnetic calorimeter. Note that 
even though the DVCS reaction has only one real photon in the final state, 
events with more than one good photon are not discarded at this stage. This is 
motivated by the fact that, while soft photons are likely to be produced in 
random coincidence, they cannot be mistaken for the large energy DVCS photons 
($>2$ GeV). The most energetic photon is always considered as the DVCS photon 
candidate.

To ensure the interaction occurs at the partonic level and the DVCS handbag 
diagram is dominant, we select events with $Q^{2}$ greater than 1 
GeV$^{2}/$c$^{2}$. Exclusivity of the coherent DVCS reaction is optimized by 
applying a set of cuts on the following kinematic variables: the co-planarity 
angle ($\Delta\phi$), \textit{i.e.}, the angle between the ($\gamma,\gamma^*$) 
and ($\gamma^*$,$^4$He$'$) planes, the missing energy, the missing mass 
squared, the missing transverse momentum of the $e'^4$He$'\gamma$ system, the 
missing mass squared of the $e'^4$He$'$ system, and the angle ($\theta$) 
between the measured photon and the missing momentum of the $e'^4$He$'$ system.

The experimental data for the most relevant observables and applied
cuts is shown in Fig.~\ref{fig:kin-cuts}.
%The most relevant of these cuts are presented in Fig.~\ref{fig:kin-cuts}, which 
%shows 3$\sigma$ cuts except for the missing energy (which appears to be too 
%large and for which we reduced the cut window to [-0.45,0.5] GeV).
We also 
reject events where a $\pi^0$ is identified by invariant mass reconstruction of 
two photons. About 3200 events pass these requirements. Their kinematic 
distributions are shown in Fig.~\ref{fig:kin-coverage}.

\begin{figure}[tb]
\includegraphics[width=9cm]{figs/coh_exc_cuts.pdf}
\caption{Four of the six coherent DVCS exclusivity cuts. The black 
distributions represent the coherent DVCS events candidates. The shaded 
distributions represent the events which passed all the exclusivity cuts except 
the quantity plotted. The vertical red lines represent the applied exclusivity 
cuts. The distributions from left to right and from top to bottom are: $\Delta 
\phi$, missing energy, missing mass squared and the cone angle ($\theta$) 
between the measured and the calculated photon.}
\label{fig:kin-cuts}
\end{figure}

@@

%asymmetries
In this work, the physics observable extracted using coherent DVCS events is
the beam-spin asymmetry (BSA). The BSA on an unpolarized target, $A_{LU}$, is 
measured as the difference of cross sections for the reaction with opposite beam 
helicities normalized to the total cross section:
  \begin{equation}
  A_{LU} = \frac{d^{5}\sigma^{+} - d^{5}\sigma^{-} }
                {d^{5}\sigma^{+} + d^{5}\sigma^{-}},
    \label{BSA_equation}
  \end{equation}
where $d^{5}\sigma^{+(-)}$ is the DVCS differential cross 
section for positive (negative) beam helicity. 
In this ratio, luminosity normalization and
detector efficiencies largely cancel and $A_{LU}$ can be 
extracted from the reaction yields for the two helicities ($N^{+/-}$)
%expressed in terms of helicity-state yields ($N^{+/-}$)
\begin{equation}
A_{LU} = \frac{1}{P_{B}} \frac{N^{+} - N^{-}}{N^{+} + N^{-} },
\end{equation}
where $P_{B}$ is the degree of longitudinal polarization of the incident electron beam.

The DVCS and well-known Bethe-Heitler (BH) processes, in which the real 
photon is emitted by the incoming or the outgoing lepton, have the same final 
state and are indistinguishable. The amplitude of electroproduction of real
photons includes a sum of the amplitudes of these two processes. The BH 
amplitude is defined by the target form factors, while the DVCS amplitude is 
a combination of the form factors and GPDs. For our kinematics, the cross 
section of real photon electroproduction is dominated by the BH 
contribution, while the DVCS contribution is very small. Its effect is however
enhanced in the observables sensitive to the interference term, {\it e.g.} 
BSA. The three terms entering the cross section calculation,
the square of the BH and DVCS amplitudes and their interference term, depend on the
azimuthal angle
$\phi$ between the $(e,e^\prime)$ and $(\gamma^*,^4$He$^\prime)$ planes, as
shown for the nucleon in Ref.~\cite{Belitsky:2001ns} and for the spin-zero targets
in Refs.~\cite{Kirchner:2003wt,Belitsky:2008bz}. Based on this work, the BSA 
of a spin-zero hadron can be expressed as
\begin{equation}
\begin{split}
&A_{LU}(\phi) = \\
&\frac{\alpha_{0}(\phi) \, \Im m(\mathcal{H}_{A})}
{\alpha_{1}(\phi) + \alpha_{2}(\phi) \, \Re e(\mathcal{H}_{A}) + \alpha_{3}(\phi) \, 
\big( \Re e(\mathcal{H}_{A})^{2} + \Im m(\mathcal{H}_{A})^{2} \big)},
\end{split}
\label{eq:A_LU-coh}
\end{equation}
where $\Im m(\mathcal{H}_{A})$ and $\Re e(\mathcal{H}_{A})$ are the imaginary 
and real parts of the $^4$He CFF $\mathcal{H}_{A}$ and depend on the GPD $H_A$.  
The explicit expression of the kinematic factors $\alpha_i$ are written in
Ref.~\cite{Belitsky:2008bz} and are functions of Fourier harmonics in the 
azimuthal angle $\phi$, the nuclear form factor $F_A(t)$, $Q^2$, $x_B$,
$x_{A} = \frac{x_{B}M_{N}}{M_{A}}$, $y=\frac{Q^{2}}{2x_{A}M_{A}E_{beam}}$, and 
$\epsilon = \frac{2x_{A}M_{A}}{\sqrt{Q^{2}}}$, where $M_{A}$($M_{N}$) is the $^4$He 
(nucleon) mass. Using the different $\sin(\phi)$ and $\cos(\phi)$ contributions 
in these factors, it is possible to unequivocally extract both imaginary and real 
parts of $\mathcal{H}_{A}$ from the BSA.

In this work, the azimuthal dependence of the BSA, $A_{LU}$, has been studied 
for a wide range of kinematics. We identified two main backgrounds to our 
measurement, accidental coincidences and exclusive coherent $\pi^0$ production.  
The accidentals have particles originating from different events, and we 
estimated their contribution to be 4.1\% of our sample. We evaluated this 
contribution by selecting events passing all our cuts but with an electron and 
helium originating from different vertices. The $\pi^0$ production can easily
be mistaken for DVCS when one of the two photons from the $\pi^0$ 
decay is produced at low energy in the laboratory frame and remains undetected.  
To estimate the effect of this background, we developed an event generator 
tuned on the experimental yield of exclusive $\pi^0$ measured by our 
experiment. We used this generator together with a GEANT3 simulation of our 
detector to estimate the ratio between the number of $\pi^0$ events where the 
two photons are detected and those that are misidentified as DVCS events. This 
ratio is then multiplied by the measured yield of exclusive $\pi^0$ events to 
correct the DVCS data.  Depending on the kinematics, we found contaminations of 
2 to 4\%. The study of systematic uncertainties showed that the main 
contributions come from the choice of the DVCS exclusivity cuts (8\%) and the 
large binning size (5.1\%). However, added quadratically, the total systematic 
uncertainty is about 10\%, which is significantly smaller than statistical 
uncertainties in all kinematical bins.

Due to limited statistics, dependence of the extracted asymmetries on the kinematical variables $Q^2$, 
$x_B$, and $t$ has been studied separately. In Fig.~\ref{fig:alu}, $A_{LU}$ for 
bins in each of the three variables is presented. The curves on the plots are fits with 
the function presented in Eq.~(\ref{eq:A_LU-coh}), where the real and imaginary 
parts of the CFF $\mathcal{H}_{A}$ are the free parameters of the fit.  In 
Fig.~\ref{fig:alu90} the $Q^2$, $x_{B}$, and $t$-dependencies of the fitted 
$A_{LU}$ at $\phi$~=~90$^{\circ}$ are shown. The $x_{B}$ and $t$-dependencies 
are compared to theoretical calculations performed by S.~Liuti and K.~Taneja 
\cite{simonetta_2}. The model accounts for the effect on the quark 
distribution of the virtuality (off-shellness) of the nucleon. The calculations are at slightly 
different kinematics than our data but still provide some guidance. The 
experimental results appear to have a larger asymmetries than the calculations
in the $x_B = 0.307$ bin. The difference may arise from the theoretical 
uncertainty in the determination of the crossing point between the 
antishadowing region, where the parton nuclear distribution is larger than the 
nucleon one, and the EMC effect region, where the nuclear effect reverses its 
sign.

@@

\begin{figure}[tb]
\includegraphics[width=8cm]{figs/Coherent_CFF.pdf}
\caption{The model-independent extraction of the imaginary (top panel) and
real (bottom panel) parts of the $^4$He CFF $\mathcal{H}_A$, as functions of
$Q^{2}$ (right panel), $x_B$ (middle panel), and $t$ (left panel). The full red 
curves are calculations based on an on-shell model from Ref.~\cite{Vadim_priv}.
The black-dashed curves are calculations from a convolution 
model based on the VGG model for the nucleons' GPDs \cite{Guidal_priv}. The 
blue long-dashed curve on the top-right plot is from
an off-shell model as described in Ref.~\cite{GonzalezHernandez:2012jv}.}
\label{fig:CFF_HA}
\end{figure}

The $Q^2$, $x_B$, and $t$ dependencies of the $^4$He CFF $\mathcal{H}_A$ 
extracted from the fit to the azimuthal dependence of $A_{LU}$ are shown in 
Fig.~\ref{fig:CFF_HA}. Curves on the graphs are model calculations, labelled 
{\it convolution} and {\it off-shell}. In the convolution model 
\cite{Vadim_priv}, the nucleus is assumed to be composed of non-relativistic 
nucleons, each interacting independently with the probe. The Convolution-Dual 
model is based on nucleon GPDs from the dual parametrization 
\cite{Guzey:2006xi}, where the Convolution-VGG uses nucleon GPDs  from the VGG 
model and is based on the double distributions ansatz \cite{DD_model}. The 
off-shell model is the same as in Figure \ref{fig:alu90} using an improved
GPD model for the nucleon \cite{GonzalezHernandez:2012jv}.

The results in Fig.~\ref{fig:CFF_HA} show that the extraction of the CFF
from the BSA is possible without any model dependent 
assumptions. The amplitude and the dependencies observed as a function of 
$Q^{2}$, $x_B$, and $t$ are in agreement with the theoretical expectations. One 
can see a difference between the precision of the extracted imaginary and real 
parts, which is expected from
Eq.~(\ref{eq:A_LU-coh}) because $\alpha_2$ is much smaller than $\alpha_1$. While the 
accuracy of our results does not allow to discriminate between the models, they 
demonstrate possibility of extraction of the CFF of spin 0 target in a model 
independent way.
